RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-07-25 manuscripts/manuscript.Rmd
add Francois to acknowledgements

There are many promising directions for further development of the
`RNeXML` package.  The project's [Milestones page][https://github.com/ropensci/RNeXML/issues/milestones] page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.

## Acknowledgements

This project was supported in part by a grant from the Alfred P Sloan
Foundation Grant 2013-6-22 (CB and SC), NSF Grant DBI-1306697 (CB), ... <!-- FIXME Rutger, Hilmar, add whatever you'd like to acknowledge here -->

`RNeXML` is part of the rOpenSci project, [http://ropensci.org].

>>>>

There are many promising directions for further development of the
`RNeXML` package.  The project's [Milestones page](https://github.com/ropensci/RNeXML/issues/milestones) page provides a list of
steps currently planned or under consideration.  In particular, these
milestones include increased support for interactive mode of entering data
(wizards), and support for integration of semantics defined through the
Web Ontology language (OWL), as discussed in the Challenges section.

## Acknowledgements
<!-- FIXME Rutger, Hilmar, add whatever you'd like to acknowledge here -->.

This project was supported in part by a grant from the Alfred P Sloan
Foundation Grant 2013-6-22 (CB and SC), NSF Grant DBI-1306697 (CB), ... 
We thank F. Michonneau for helpful comments on an earlier version
of this manuscript.
`RNeXML` is part of the rOpenSci project, [http://ropensci.org].
